Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-11-04 Genetic algorithms - Journal of Climate/template.tex
Removal of the custom references stylesheet.
Modifying structure.

\section{Optimization using Genetic algorithms}
\label{sec:gas}

Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches. These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.

@@

\begin{figure}[htb]
	\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

@@

\subsection{Recommendations of parametrization}

@@

\subsubsection{Comparison process and results}

@@

\subsubsection{Recommended parametrization of GAs}

@@

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
% \bibliographystyle{ametsoc2014}
% \bibliography{references}

\bibliographystyle{ametsoc2014_no_url}
% \bibliography{references}
\bibliography{../_refs/_articles-gas}

>>>>

\section{Assessed Genetic Algorithms variants}
\label{sec:gas}

Genetic Algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches. These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.

@@

\begin{figure}[htb]
	\noindent\includegraphics[width=19pc,angle=0]{figures/figure_structure_gas.pdf}\\
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

@@

\section{Recommendations of parametrization}

@@

\subsection{Comparison process and results}

@@

\subsection{Recommended parametrization of GAs}

@@

%% Important!
%\appendcaption{<appendix letter and number>}{<caption>} 
%must be used for figures and tables in appendixes, e.g.,
%
%\begin{figure}
%\noindent\includegraphics[width=19pc,angle=0]{figure01.pdf}\\
%\appendcaption{A1}{Caption here.}
%\end{figure}
%
% All appendix figures/tables should be placed in order AFTER the main figures/tables, i.e., tables, appendix tables, figures, appendix figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make your BibTeX bibliography by using these commands:
\bibliographystyle{ametsoc2014}
% \bibliography{references}
\bibliography{../_refs/_articles-gas}
